On Secure Delegation of SampBQP with a Classical Client

### 2020-02-05 preliminaries.tex
Move dfn proto IND-CPA

@@

We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which relates the ground state of Hamiltonians $H_1 + H_2$ with the ground state of $H_1\big|_{\ker H_2}$.

@@

We also use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client.

@@

Now we present the quantum homomorphic encryption scheme in \cite{mahadev_qfhe}.
It admits a classical client; one could do the encryption classically, and the decryption is compatible with $X$ and $Z$ measurements.
In general, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then it can be used as a compiler to achieve blindness.

@@

\subsection{Security definition for interactive protocols}

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{proto:indcpa}
	\begin{enumerate}
		\item The challenge picks $b\in\set{0,1}$ at random
		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\item $\cA$ attempts to guess $b$
	\end{enumerate}
\end{protocol}

>>>>

\subsection{Semantic security for interactive protocols}

We present the security definition for interactive protocols:

\begin{protocol}{Attack against semantic security}
	\label{proto:indcpa}
	\begin{enumerate}
		\item The challenge picks $b\in\set{0,1}$ at random
		\item If $b=0$, the challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\item Otherwise, the challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\item $\cA$ attempts to guess $b$
	\end{enumerate}
\end{protocol}

@@

We use the projection lemma from \cite{kempe_kitaev_regev_2006}, which describes the conditions under which we can estimate the ground state energy of $H_1 + H_2$ with that of $H_1\big|_{\ker H_2}$.

@@

We use the quantum fully homomorphic encryption scheme given in \cite{mahadev_qfhe} which is compatible with our use of a classical client. We start by presenting the interface of a homomorphic encryption scheme:

@@

The quantum homomorphic encryption scheme in \cite{mahadev_qfhe} has additional properties that facilitates the use of a classical clients as below:

@@

As we will see, if a given protocol has classical inputs and uses only $X$ and $Z$ measurements, then $\mathsf{QHE}$ can be used as a compiler to achieve blindness.
